---
title: "Graphs"
output: html_document
date: "2025-01-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r setup, include=FALSE}
options(packrat.dependency.discovery.renv = TRUE)
require(ggplot2)
require(ggthemes)
#require(plyr)
require(stargazer)
require(RColorBrewer)
require(scales)
require(gtable)
require(gridExtra)
require(data.table)
require(dplyr)
require(ggplot2)
require(readr)
require(tidyr)
require(lme4)
require(MASS)
library(daewr)
library(MASS)
library(GAD)
library(dplyr)
library(sjPlot)
library(blmeco)
```

```{r}
dswithrepAbbECM$CollagenI <- relevel(factor(dswithrepAbbECM$CollagenI, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$CollagenIV <- relevel(factor(dswithrepAbbECM$CollagenIV, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$Hyaluronic_Acid <- relevel(factor(dswithrepAbbECM$Hyaluronic_Acid, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$TenascinC <- relevel(factor(dswithrepAbbECM$TenascinC, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$Laminin <- relevel(factor(dswithrepAbbECM$Laminin, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$Fibronectin <- relevel(factor(dswithrepAbbECM$Fibronectin, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$Galectin3 <- relevel(factor(dswithrepAbbECM$Galectin3, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$Osteopontin <- relevel(factor(dswithrepAbbECM$Osteopontin, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)
dswithrepAbbECM$Decorin <- relevel(factor(dswithrepAbbECM$Decorin, levels = c(0, 0.25, 0.5, 0.75, 1)), ref = 1)

dswithrepAbbECM$Metadata_Treatment[dswithrepAbbECM$Metadata_Treatment == "LD"] <- "10 uM"
dswithrepAbbECM$Metadata_Treatment[dswithrepAbbECM$Metadata_Treatment == "HD"] <- "20 uM"

dswithrepAbbECM$Metadata_Treatment <- factor(dswithrepAbbECM$Metadata_Treatment, levels = c("DMSO", "10 uM", "20 uM"))
```


### EdU Findings
```{r}
EdUECMmeansNuc <- dswithrepAbbECM  %>% group_by(Metadata_Stiffness, Abb_ECMs, Laminin, CollagenI, CollagenIV, Hyaluronic_Acid, Fibronectin, Decorin, Osteopontin, Galectin3, TenascinC, Metadata_Treatment) %>% summarize(Percent_Positive = mean(Mean_Percent_Positive, na.rm = TRUE), Mean_Nuclei = mean(Mean_Nuclei, na.rm = TRUE), SEM = sd(Mean_Percent_Positive)/sqrt(length(Mean_Percent_Positive)), .groups = "drop")
```
#### Significant S:R
Lam
```{r}
interaction.plot(dswithrepAbbECM$Laminin, dswithrepAbbECM$Metadata_Stiffness, response = dswithrepAbbECM$Mean_Percent_Positive, xlab = "Ratio of Laminin", ylab = "Mean % EdU Positive", trace.label = "Stiffness")

library(ggprism)

EdUECMmeansNuc %>% group_by(Metadata_Stiffness, Laminin) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Laminin, y = Percent_Positive, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness, ), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("Ratio of Laminin")+
  ylab("% Positive EdU")+
  scale_color_manual(values = c("#db6d22", "#2100bb"))

  ggsave("StiffnessvsLamEdU.png")
```



#### Significant T:E
```{r}
interaction.plot(dswithrepAbbECM$Abb_ECMs, dswithrepAbbECM$Metadata_Treatment, response = dswithrepAbbECM$Mean_Percent_Positive, xlab = "ECM Composition", ylab = "Mean % EdU Positive", trace.label = "Treatment")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Abb_ECMs) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Abb_ECMs, y = Percent_Positive, col = Metadata_Treatment))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))
```

#### Significant T:R
LN, OPN
```{r}
interaction.plot(dswithrepAbbECM$Laminin, dswithrepAbbECM$Metadata_Treatment, response = dswithrepAbbECM$Mean_Percent_Positive, xlab = "Ratio of Laminin", ylab = "Mean % EdU Positive")

interaction.plot(dswithrepAbbECM$Osteopontin, dswithrepAbbECM$Metadata_Treatment, response = dswithrepAbbECM$Mean_Percent_Positive, xlab = "Ratio of Osteopontin", ylab = "Mean % EdU Positive", trace.label = "Treatment")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Laminin) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Laminin, y = Percent_Positive, col = Metadata_Treatment))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Laminin")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Osteopontin) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Osteopontin, y = Percent_Positive, col = Metadata_Treatment))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Osteopontin")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")
```


#### Significant R:E
C1, HA, G3
```{r}
# dswithrepAbbECM %>% filter(CollagenI != 0) %>% interaction.plot(Abb_ECM, CollagenI, response = Mean_Percent_Positive, xlab = "ECM Condition", ylab = "Mean % EdU Positive")
# 
# dswithrepAbbECM %>% filter(Hyaluronic_Acid != 0) %>% interaction.plot(Abb_ECM, Hyaluronic_Acid, response = Mean_Percent_Positive, xlab = "ECM Condition", ylab = "Mean % EdU Positive")
# 
# dswithrepAbbECM %>% filter(Galectin3 != 0) %>% interaction.plot(Abb_ECM, Galectin3, response = Mean_Percent_Positive, xlab = "ECM Condition", ylab = "Mean % EdU Positive")

EdUECMmeansNuc %>% filter(CollagenI != 0) %>% group_by(Abb_ECMs, CollagenI) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Abb_ECMs, y = Percent_Positive, col = CollagenI))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = CollagenI, linetype = CollagenI), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
  labs(color = "Collagen I")+
  scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")
ggsave("CollagenIRatiovsECMEdU.png", width = 10, height = 5)

EdUECMmeansNuc %>% filter(Hyaluronic_Acid != 0) %>% group_by(Abb_ECMs, Hyaluronic_Acid) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Abb_ECMs, y = Percent_Positive, col = Hyaluronic_Acid))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Hyaluronic_Acid, linetype = Hyaluronic_Acid), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")
ggsave("HARatiovsECMEdU.png", width = 10, height = 5)

EdUECMmeansNuc %>% filter(Galectin3 != 0) %>% group_by(Abb_ECMs, Galectin3) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Abb_ECMs, y = Percent_Positive, col = Galectin3))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Galectin3, linetype = Galectin3), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
 scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")
ggsave("G3RatiovsECMEdU.png", width = 10, height = 5)
```



#### Significant Stiffness:Treatment:Raio
LN, G3

```{r}
# dswithrepAbbECM %>% filter(Metadata_Stiffness == "1kPa") %>% interaction.plot(Laminin, Metadata_Treatment, response = Mean_Percent_Positive, xlab = "Ratio of Laminin", ylab = "Mean % EdU Positive", trace.label = "Treatment")
# 
# dswithrepAbbECM %>% filter(Metadata_Stiffness == "25kPa") %>% interaction.plot(Laminin, Metadata_Treatment, response = Mean_Percent_Positive, xlab = "Ratio of Laminin", ylab = "Mean % EdU Positive", trace.label = "Treatment")
# 
# dswithrepAbbECM %>% filter(Metadata_Stiffness == "1kPa") %>% interaction.plot(Galectin3, Metadata_Treatment, response = Mean_Percent_Positive, xlab = "Ratio of Galectin 3", ylab = "Mean % EdU Positive", trace.label = "Treatment")
# 
# dswithrepAbbECM %>% filter(Metadata_Stiffness == "25kPa") %>% interaction.plot(Galectin3, Metadata_Treatment, response = Mean_Percent_Positive, xlab = "Ratio of Galectin 3", ylab = "Mean % EdU Positive", trace.label = "Treatment")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Laminin, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Laminin, y = Percent_Positive, col = Metadata_Treatment))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Laminin")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Laminin, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Metadata_Treatment, y = Percent_Positive, col = Laminin ))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Laminin), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Galectin3, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Galectin3, y = Percent_Positive, col = Metadata_Treatment))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Galectin3")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Galectin3, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Galectin3, y = Percent_Positive, col = Metadata_Stiffness))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Galectin3")+
  ylab("% Positive EdU")+
  scale_color_manual(values = c("#db6d22", "#2100bb"))

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Galectin3, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Metadata_Treatment, y = Percent_Positive, col = Galectin3 ))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Galectin3), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")

```

#### Significant Treatment:Ratio:ECMs
C1, C4, HA, TC, FN

would be really crowded and not interpretable... Choose a couple examples
```{r}
dswithrepAbbECM %>% filter(CollagenI != 0) %>% interaction.plot(Abb_ECM, CollagenI, response = Mean_Percent_Positive, xlab = "ECM Condition", ylab = "Mean % EdU Positive")
```

```{r}
library(ggpubr)

C1TEsig <- compare_means(Mean_Percent_Positive ~ Metadata_Treatment, subset(dswithrepAbbECM, CollagenI != 0 & Metadata_Stiffness == "1kPa"), group.by = c("CollagenI", "Abb_ECMs"))

C4TEsig <- compare_means(Mean_Percent_Positive ~ Metadata_Treatment, subset(dswithrepAbbECM, CollagenIV != 0& Metadata_Stiffness == "1kPa"), group.by = c("CollagenIV", "Abb_ECMs"))

HATEsig <-compare_means(Mean_Percent_Positive ~ Metadata_Treatment,subset(dswithrepAbbECM, Hyaluronic_Acid != 0& Metadata_Stiffness == "1kPa"), group.by = c("Hyaluronic_Acid", "Abb_ECMs"))

TCTEsig <-compare_means(Mean_Percent_Positive ~ Metadata_Treatment,subset(dswithrepAbbECM, TenascinC != 0& Metadata_Stiffness == "1kPa"), group.by = c("TenascinC", "Abb_ECMs"))

FNTEsig <-compare_means(Mean_Percent_Positive ~ Metadata_Treatment, subset(dswithrepAbbECM, Fibronectin != 0& Metadata_Stiffness == "1kPa"),group.by = c("Fibronectin", "Abb_ECMs"))
```

```{r}
EdUECMmeansNuc %>% group_by(Metadata_Treatment, Abb_ECMs, TenascinC) %>% filter(TenascinC != 0) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Abb_ECMs, y = Percent_Positive, col = TenascinC))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = TenascinC, linetype = TenascinC), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle("Ratio of Tenascin C Over Treatment and ECMs")

ggsave("TCTreatECMEdU.png")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Abb_ECMs, Fibronectin) %>% filter(Fibronectin != 0) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Abb_ECMs, y = Percent_Positive, col = Fibronectin))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = Fibronectin, linetype = Fibronectin), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
   scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle("Ratio of Fibronectin Over Treatment and ECMs")
ggsave("FNTreatECMEdU.png")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Abb_ECMs, Hyaluronic_Acid) %>% filter(Hyaluronic_Acid != 0) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Abb_ECMs, y = Percent_Positive, col = Hyaluronic_Acid))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = Hyaluronic_Acid, linetype = Hyaluronic_Acid), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
   scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle("Ratio of Hyaluronic Acid Over Treatment and ECMs")
ggsave("HATreatECMEdU.png")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Abb_ECMs, CollagenIV) %>% filter(CollagenIV != 0) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Abb_ECMs, y = Percent_Positive, col = CollagenIV))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = CollagenIV, linetype = CollagenIV), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
   scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle("Ratio of Collagen IV Over Treatment and ECMs")
ggsave("C4TreatECMEdU.png")

EdUECMmeansNuc %>% group_by(Metadata_Treatment, Abb_ECMs, CollagenI) %>% filter(CollagenI != 0) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Abb_ECMs, y = Percent_Positive, col = CollagenI))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = CollagenI, linetype = CollagenI), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
   scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle("Ratio of Collagen I Over Treatment and ECMs")
ggsave("C1TreatECMEdU.png")
```


##### Boxplot TCHA & C1HA

```{r}
dswithrepAbbECM$Metadata_Treatment[dswithrepAbbECM$Metadata_Treatment == "LD"] <- "10 uM"
dswithrepAbbECM$Metadata_Treatment[dswithrepAbbECM$Metadata_Treatment == "HD"] <- "20 uM"

dswithrepAbbECM$Metadata_Treatment <- factor(dswithrepAbbECM$Metadata_Treatment, levels = c("DMSO", "10 uM", "20 uM"))

ratiocomparisons <- list(c("0.25", "0.5"), c("0.25","0.75"),c("0.5", "0.75"))

dswithrepAbbECM %>% filter(Abb_ECMs == "TCHA") %>% ggplot(aes(x = TenascinC, y = Mean_Percent_Positive))  +
  facet_grid(cols = vars(Metadata_Treatment)) +
  geom_boxplot( fill = "#94d8d8")+
  stat_compare_means(comparisons = ratiocomparisons, label = "p.signif")+
  theme_prism(border = TRUE)+
  xlab("Ratio of Tenascin C")+
  ylab("Mean % EdU Positive") +
  ggtitle("TC:HA ECM Combinations") 

ggsave("TCHABoxEdU.png", width = 10, height = 5)


 EdUECMmeansNuc %>% filter(Abb_ECMs == "TCHA") %>% group_by(Metadata_Treatment, TenascinC) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Metadata_Treatment, y = Percent_Positive, col = TenascinC))+
 # facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = TenascinC), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("TC:HA ECM Combinations")
 
 EdUECMmeansNuc %>% filter(Abb_ECMs == "C1HA") %>% group_by(Metadata_Treatment, CollagenI) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Metadata_Treatment, y = Percent_Positive, col = CollagenI))+
 # facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = CollagenI), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("C1:HA ECM Combinations")

```
## Profiles from Heatmap
```{r}
 
 EdUECMmeansNuc %>% filter(Abb_ECMs == "FN") %>% filter(Fibronectin == 1) %>% group_by(Metadata_Treatment, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Metadata_Treatment, y = Percent_Positive, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("FN100 ECM Combinations")

EdUECMmeansNuc %>% filter(Abb_ECMs == "DNFN") %>% filter(Fibronectin == 0.5) %>% group_by(Metadata_Treatment, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Metadata_Treatment, y = Percent_Positive, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("50:50 DNFN ECM Combinations")

EdUECMmeansNuc %>% filter(Abb_ECMs == "LNDN") %>% filter(Laminin == 0.25) %>% group_by(Metadata_Treatment, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Metadata_Treatment, y = Percent_Positive, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("25:75 LNDN ECM Combinations")

EdUECMmeansNuc %>% filter(Abb_ECMs == "LNHA") %>% filter(Laminin == 0.5) %>% group_by(Metadata_Treatment, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Metadata_Treatment, y = Percent_Positive, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("50:50 LNHA ECM Combinations")

EdUECMmeansNuc %>% filter(Abb_ECMs == "C4") %>% filter(CollagenIV == 1) %>% group_by(Metadata_Treatment, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Metadata_Treatment, y = Percent_Positive, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
   ggtitle("C4100 ECM Combinations")
```


## Treatment Box
stiffness 1 kPa = #db6d22, 25 kPa = #2100bb
```{r}
treatmentcomp <- list(c("DMSO", "10 uM"), c("DMSO", "20 uM"), c("10 uM", "20 uM"))
dswithrepAbbECM %>% ggplot(aes(Metadata_Treatment, Mean_Percent_Positive)) +
  geom_boxplot()+
  theme_prism()+
  stat_compare_means(comparisons = treatmentcomp)

dswithrepAbbECM %>% ggplot(aes(Metadata_Stiffness, Mean_Percent_Positive)) +
  geom_boxplot()+
  theme_prism()+
  stat_compare_means()

treatmentcomp <- list(c("DMSO", "10 uM"), c("DMSO", "20 uM"), c("10 uM", "20 uM"))

dswithrepAbbECM %>% ggplot(aes(Metadata_Treatment, Mean_Percent_Positive, fill = Metadata_Stiffness)) +
  geom_boxplot()+
  theme_prism()+
  stat_compare_means(label = "p.signif", size = 5)+
  scale_fill_manual(values = c("#db6d22", "#2100bb"))+
  xlab("Sorafenib Treatment")+
  ylab("% EdU Positive")
ggsave("EdUTreatStiffBox.png")
```

```{r}
EdUECMmeansNuc %>% group_by(Metadata_Treatment, Metadata_Stiffness) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot( aes(x = Metadata_Treatment, y = Percent_Positive, col = Metadata_Stiffness))+
 # facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Treatment")+
  ylab("% Positive EdU")+
   
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" ))

```
## Need to  Figure out Survival
```{r}
FOCsumm <- FOC %>% group_by(Abb_ECMs, Metadata_Stiffness, Metadata_Treatment, CollagenI,CollagenIV, Laminin, Hyaluronic_Acid,   TenascinC, Osteopontin, Galectin3, Fibronectin, Decorin, Conditions)%>% summarize(FOC = mean(FOC), ControlMean = mean(ControlMean))
```
"C1:DN"  "C1:HA"  "C4:FN"  "C4:G3"  "C4:LN"  "C4:OPN" "G3:FN"  "HA:DN"  "HA:FN"  "LN:DN"  "LN:FN"  "LN:G3"  "OPN:G3" Maintained

```{r}
FOCDecreased <- subset(FOCsumm, FOC < 0.25)
FOCMaintained <- subset(FOCsumm, 0.75<FOC & FOC<1.25)

FOCMaintained <- subset(FOCMaintained, Metadata_Treatment != "DMSO")


hist(subset(FOCsumm, Metadata_Treatment != "DMSO")$FOC, breaks = 30)

```

##P Heatmap
```{r}
heatmapEdU <- FOC[,c("Abb_ECMs", "Metadata_Slide", "Metadata_Experiment", "Metadata_Ratio", "Metadata_Stiffness", "Metadata_Treatment", "Mean_Percent_Positive")]

heatmapEdU <- heatmapEdU %>% group_by(Abb_ECMs, Metadata_Stiffness, Metadata_Treatment, Metadata_Ratio)%>%summarize(Mean_EdU = mean(Mean_Percent_Positive), .groups = "drop")

heatmapEdU <- heatmapEdU %>% mutate(TreatStiffness = paste(Metadata_Treatment, Metadata_Stiffness), Microenvironment = paste0(Abb_ECMs, Metadata_Ratio))

heatmapEdU <- heatmapEdU[,c("TreatStiffness" ,"Microenvironment", "Mean_EdU")]

heatmapEdU <- pivot_wider(data = heatmapEdU, names_from = "TreatStiffness", values_from = c("Mean_EdU"))
 
heatmapEdU <- as.matrix(heatmapEdU)

rownames(heatmapEdU) <- heatmapEdU[,1]

heatmapEdU <- heatmapEdU[,2:7]

heatmapEdU<- as.matrix(heatmapEdU)

class(heatmapEdU) <- "numeric"
```


```{r}
colannEdU <- c("DMSO 1kPa" ,  "10 uM 1kPa" , "20 uM 1kPa" , "DMSO 25kPa","10 uM 25kPa", "20 uM 25kPa")

colEdUdf <- data.frame(TreatStiff = colannEdU)

colEdUdf <- colEdUdf %>% mutate(Treatment = case_when(TreatStiff %in% c("10 uM 1kPa",  "10 uM 25kPa") ~ "10 uM", 
                                                      TreatStiff %in% c("20 uM 1kPa",  "20 uM 25kPa") ~ "20 uM",
                                                      TreatStiff %in% c("DMSO 1kPa",  "DMSO 25kPa") ~ "DMSO"), 
                                            
Stiffness = if_else(TreatStiff %in% c("DMSO 1kPa", "10 uM 1kPa" , "20 uM 1kPa"), "1kPa", "25kPa"))
  
colEdUgrouping <- data.frame(Treatment = colEdUdf[,2],  Stiffness = colEdUdf[,3], row.names = colEdUdf[,1])
```

```{r}
library(pheatmap)

pheatmap(heatmapEdU, color = colorRampPalette(rev(brewer.pal(n=7, name = "PRGn")))(100), angle_col = 45, height = 15, width = 5, fontsize_row = 10, annotation_col = colEdUgrouping, annotation_colors = list(
  Treatment = c("DMSO" = "#D9DDDC", "10 uM" = "#6c6768", "20 uM" = "#000000"), 
  Stiffness = c("1kPa" = "#db6d22", "25kPa" = "#2100bb")), filename = "EdUheatmapcol.png")

pheatmap(heatmapEdU, color = colorRampPalette(rev(brewer.pal(n=7, name = "PRGn")))(100), angle_col = 45, height = 15, width = 5, cluster_cols = FALSE, fontsize_row = 10, 
         annotation_col = colEdUgrouping, annotation_colors = list(
 Treatment = c("DMSO" = "#D9DDDC", "10 uM" = "#6c6768", "20 uM" = "#000000"), 
  Stiffness = c("1kPa" = "#db6d22", "25kPa" = "#2100bb")),
         filename = "EdUheatmapnone.png")

```


```{r}
library(ggprism)
FOCsumm %>% filter(Metadata_Treatment != "DMSO") %>% ggplot(aes(ControlMean, FOC, color = Conditions)) + 
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness))+
  geom_point()+
  theme_prism() +
  theme(legend.position = "none")
  
```
"C1:DN"  "C1:HA"  "C4:FN"  "C4:G3"  "C4:LN"  "C4:OPN" "G3:FN"  "HA:DN"  "HA:FN"  "LN:DN"  "LN:FN"  "LN:G3"  "OPN:G3" Maintained

```{r}
FOCDecreased1 <- FOCDecreased %>% filter(Metadata_Stiffness == "1kPa")
FOCDecreased25 <- FOCDecreased %>% filter(Metadata_Stiffness == "25kPa")
```

```{r}
ECMcomp<- ggpubr::compare_means(Mean_Nuclei ~ Metadata_Ratio, dswithrepAbbECM, group.by = c("Metadata_Treatment", "Abb_ECMs") )

Treatcomp <- ggpubr::compare_means(Mean_Nuclei ~ Metadata_Treatment, subset(dswithrepAbbECM, Metadata_Treatment != "DMSO"), group.by = "Conditions" )

FOCTreatcomp <- compare_means(FOC ~ Metadata_Treatment, subset(FOC, Metadata_Treatment != "DMSO"), group.by = "Conditions")
```

```{r}
library(ggpubr)
dswithrepAbbECM %>% filter(Metadata_Treatment == "LD") %>% filter(Abb_ECMs == "HAG3") %>% ggplot(aes(Metadata_Ratio, Mean_Nuclei)) + 
  geom_boxplot()+
  theme_prism()+
  stat_compare_means(comparisons = list(c("25/75", "50/50"), c("25/75", "75/25"), c("75/25", "50/50")), label = "p.signif")
```

