---
title: "Survival Plots"
output: html_document
date: "2025-01-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
options(packrat.dependency.discovery.renv = TRUE)
require(ggplot2)
require(ggthemes)
#require(plyr)
require(stargazer)
require(RColorBrewer)
require(scales)
require(gtable)
require(gridExtra)
require(data.table)
require(dplyr)
require(ggplot2)
require(readr)
require(tidyr)
require(lme4)
require(MASS)
library(daewr)
library(MASS)
library(GAD)
library(dplyr)
library(sjPlot)
library(blmeco)
library(ggpubr)
library(ggprism)
```

```{r}
dswithrepAbbECM$Metadata_Treatment[dswithrepAbbECM$Metadata_Treatment == "LD"] <- "10 uM"
dswithrepAbbECM$Metadata_Treatment[dswithrepAbbECM$Metadata_Treatment == "HD"] <- "20 uM"

dswithrepAbbECM$Metadata_Treatment <- factor(dswithrepAbbECM$Metadata_Treatment, levels = c("DMSO", "10 uM", "20 uM"))
```

## Treatment and Stiffness
```{r}
treatmentcomp <- list(c("DMSO", "10 uM"), c("DMSO", "20 uM"), c("10 uM", "20 uM"))
dswithrepAbbECM %>% ggplot(aes(Metadata_Treatment, Mean_Nuclei)) +
  geom_boxplot()+
  theme_prism()+
  xlab("Sorafenib Treatment")+
  ylab("Average Adhesion")+
  stat_compare_means(comparisons = treatmentcomp, label = "p.signif")

dswithrepAbbECM %>% ggplot(aes(Metadata_Stiffness, Mean_Nuclei, fill = Metadata_Stiffness)) +
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_boxplot()+
  theme_prism()+
  xlab("Stiffness")+
  ylab("Average Adhesion")+
  scale_fill_manual(values = c("#db6d22", "#2100bb"))+
  stat_compare_means(comparisons = list(c("1kPa", "25kPa")), label = "p.signif", size =7, vjust = 0.5)
ggsave("StiffnessbyTreatmentinSur.png")
```

```{r}
dswithrepAbbECM %>% group_by(Metadata_Stiffness, Metadata_Treatment) %>% summarize(Mean_Nuclei = mean(Mean_Nuclei)) %>%ggplot( aes(x = Metadata_Treatment, y = Mean_Nuclei, col = Metadata_Stiffness))+
  #facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Stiffness), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Sorafenib Treatment")+
  ylab("Average Cell Number")+
  scale_color_manual(values  = c("darkorange", "blue" ))
```
### FOC Full Treatment Range
```{r}
FOC %>% filter(Metadata_Treatment != "DMSO") %>% group_by(Condition, Metadata_Treatment, Metadata_Stiffness)%>% #summarize(ControlMean = mean(ControlMean), FOC = mean(FOC)) %>% 
  ggplot(aes(ControlMean, FOC, color = Condition))+
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness)) + 
  geom_point()+
  ylab("Drug/DMSO Control (Survival)")+
  xlab("Cell Number DMSO Control")+
  theme_prism(border = TRUE)+
  geom_hline(yintercept = 1)+
  geom_hline(yintercept = 0.5)+
  theme(legend.position = "none")
ggsave("FOCScatter.png", dpi = 1200)

FOC %>% filter(Metadata_Treatment != "DMSO")%>% group_by(Condition, Metadata_Treatment, Metadata_Stiffness)%>% #summarize(ControlMean = mean(ControlMean), FOC = mean(FOC)) %>% 
  ggplot(aes(ControlMean, FOC, color = Condition))+
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness)) + 
  geom_point()+
  scale_y_log10()+
  ylab("Drug/DMSO Control (Survival)")+
  xlab("Cell Number DMSO Control")+
  theme_prism(border = TRUE)+
  geom_hline(yintercept = 1)+
  geom_hline(yintercept = 0.5)+
  theme(legend.position = "none")
ggsave("FOCScatterlog.png", dpi = 1200)
```

### FOC 20 uM Only
```{r}
FOC %>% filter(Metadata_Treatment == "20 uM") %>% group_by(Condition, Metadata_Treatment, Metadata_Stiffness)%>%
  #summarize(ControlMean = mean(ControlMean), FOC = mean(FOC)) %>% 
  ggplot(aes(ControlMean, FOC, color = Condition))+
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness)) + 
  geom_point()+
  ylab("Drug/DMSO Control (Survival)")+
  xlab("Cell Number DMSO Control")+
  theme_prism(border = TRUE)+
  geom_hline(yintercept = 1)+
  geom_hline(yintercept = 0.5)+
  theme(legend.position = "none")
ggsave("FOCScatter20.png", dpi = 1200)

FOC %>% filter(Metadata_Treatment == "20 uM")%>% group_by(Condition, Metadata_Treatment, Metadata_Stiffness)%>% #summarize(ControlMean = mean(ControlMean), FOC = mean(FOC)) %>% 
  ggplot(aes(ControlMean, FOC, color = Condition))+
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness)) + 
  geom_point()+
  scale_y_log10()+
  ylab("Drug/DMSO Control (Survival)")+
  xlab("Cell Number DMSO Control")+
  theme_prism(border = TRUE)+
  geom_hline(yintercept = 1)+
  geom_hline(yintercept = 0.5)+
  theme(legend.position = "none")
ggsave("FOCScatterlog20.png", dpi = 1200)
```

Calculating Numbers for Dots (If Needed)
## 10 uM over both stiffnesses
```{r}
FOCsumm %>%filter(Metadata_Stiffness == "1kPa")%>% filter(Metadata_Treatment == "10 uM")%>% filter(FOC < 0.5)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "1kPa")%>% filter(Metadata_Treatment == "10 uM")%>% filter(FOC > 0.5 & FOC < 1)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "1kPa")%>% filter(Metadata_Treatment == "10 uM")%>% filter(FOC > 1)%>% nrow()

FOCsumm %>%filter(Metadata_Stiffness == "25kPa")%>% filter(Metadata_Treatment == "10 uM")%>% filter(FOC < 0.5)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "25kPa")%>% filter(Metadata_Treatment == "10 uM")%>% filter(FOC > 0.5 & FOC < 1)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "25kPa")%>% filter(Metadata_Treatment == "10 uM")%>% filter(FOC > 1)%>% nrow()
```

## 20 uM over both stiffnesses
```{r}
FOCsumm %>%filter(Metadata_Stiffness == "1kPa")%>% filter(Metadata_Treatment == "20 uM")%>% filter(FOC < 0.5)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "1kPa")%>% filter(Metadata_Treatment == "20 uM")%>% filter(FOC > 0.5 & FOC < 1)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "1kPa")%>% filter(Metadata_Treatment == "20 uM")%>% filter(FOC > 1)%>% nrow()

FOCsumm %>%filter(Metadata_Stiffness == "25kPa")%>% filter(Metadata_Treatment == "20 uM")%>% filter(FOC < 0.5)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "25kPa")%>% filter(Metadata_Treatment == "20 uM")%>% filter(FOC > 0.5 & FOC < 1)%>% nrow()

FOCsumm %>% filter(Metadata_Stiffness == "25kPa")%>% filter(Metadata_Treatment == "20 uM")%>% filter(FOC > 1)%>% nrow()
```

### Making a Dataframe for Bar Plot
```{r}
SurFOC <- data.frame(Count = c(62,52,3,100,16,1,88,28,1,116,1,0), Stiffness = c("1kPa","1kPa","1kPa","25kPa","25kPa","25kPa","1kPa","1kPa","1kPa","25kPa","25kPa","25kPa"), Treatment = c("10 uM","10 uM","10 uM","10 uM","10 uM","10 uM","20 uM","20 uM","20 uM","20 uM","20 uM","20 uM"), Assignment  = c("FOC<0.5", "0.5<FOC<1", "FOC>1", "FOC<0.5", "0.5<FOC<1", "FOC>1","FOC<0.5", "0.5<FOC<1", "FOC>1","FOC<0.5", "0.5<FOC<1", "FOC>1") )

SurFOC$Assignment <- factor(SurFOC$Assignment, levels = c( "FOC>1", "0.5<FOC<1", "FOC<0.5")) 
```

```{r}
SurFOC %>% mutate(StiffTreat = paste(Stiffness, Treatment))%>% ggplot(aes(x = StiffTreat, y = Count, fill = Assignment))+
  geom_col(position = "dodge")
```


## Stiffness and Treatment Plots
```{r}
FOC %>% filter(Metadata_Treatment != "DMSO") %>% ggplot(aes(x = Metadata_Stiffness, y = FOC)) + 
  geom_boxplot()+
  theme_prism()+
  stat_compare_means()+
  scale_y_log10()+
  xlab("Stiffness")+
  ylab("Fraction of DMSO Control")+
stat_summary(fun = "mean", color = "red", pch = 8)
ggsave("FOCStiff.png", height = 3.5, width = 7)

FOC %>% filter(Metadata_Treatment != "DMSO") %>% ggplot(aes(x = Metadata_Treatment, y = FOC)) + 
  geom_boxplot()+
  theme_prism()+
 stat_compare_means()+
  scale_y_log10()+
   xlab("Sorafenib Treatment")+
  ylab("Fraction of DMSO Control")+
  stat_summary(fun = "mean", color = "red", pch = 8)
ggsave("FOCTreat.png", height = 3.5, width = 7)

FOC$Metadata_Treatment <- factor(FOC$Metadata_Treatment, levels = c("DMSO", "10 uM", "20 uM"))

FOC %>% ggplot(aes(x = Metadata_Stiffness, y = FOC, fill = Metadata_Stiffness)) + 
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_boxplot()+
  theme_prism()+
 stat_compare_means(comparisons = list(c("1kPa", "25kPa")),label = "p.signif", size = 7, hide.ns = TRUE, vjust = 0.5)+
  scale_fill_manual(values = c("#db6d22", "#2100bb"))+
   xlab("Stiffness (kPa)")+
  ylab("Fraction of DMSO Control")
 # stat_summary(fun = "mean", color = "red", pch = 8)
ggsave("FOCTreatStiff.png", height = 5, width = 10)
```

## Interaction Plots
stiffness 1 kPa = #db6d22, 25 kPa = #2100bb
ratio "#8dc1e1","#0f99ca","#07709f" 'solid' 1, 'dashed' 2, 'dotdash' 4
```{r}
FOCECMmeansNuc <- FOC  %>% filter(Metadata_Treatment != "DMSO") %>% group_by(Metadata_Stiffness, Abb_ECMs, Laminin, CollagenI, CollagenIV, Hyaluronic_Acid, Fibronectin, Decorin, Osteopontin, Galectin3, TenascinC, Metadata_Treatment) %>% summarize(FOC = mean(FOC, na.rm = TRUE), SEM = sd(FOC)/sqrt(length(FOC)), .groups = "drop")
```

### Stiff:Treat:Galectin3
```{r}
FOCECMmeansNuc %>% group_by(Metadata_Stiffness, Metadata_Treatment, Galectin3) %>% summarize(FOC = mean(FOC)) %>%ggplot( aes(x = Galectin3, y = FOC, col = Metadata_Treatment))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment, linetype = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Galectin 3")+
  ylab("Survival")+
  scale_color_manual(values  = c( "#fa7152","#c9462d","#8dc1e1","#0f99ca","#07709f")) +
  scale_linetype_manual(values = c("solid", "dashed"))+
  ggtitle("Stiffness:Treatment Interactions On Galectin 3 Ratios")

 ggsave("StiffnessTreatG3FOC.png")
 
 FOCECMmeansNuc %>% group_by(Metadata_Stiffness, Metadata_Treatment, Galectin3) %>% summarize(FOC = mean(FOC)) %>%ggplot( aes(x = Galectin3, y = FOC, col = Metadata_Treatment))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Metadata_Treatment, linetype = Metadata_Treatment), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("Ratio of Galectin 3")+
  ylab("Survival")+
  scale_color_manual(values  = c( "#fa7152","#c9462d","#8dc1e1","#0f99ca","#07709f")) +
  scale_linetype_manual(values = c("solid", "dashed"))+
  ggtitle("Stiffness:Treatment Interactions On Galectin 3 Ratios")

 ggsave("StiffnessTreatG3FOC.png")
```
```{r}
FOCECM %>% group_by(Metadata_Treatment, Abb_ECMs, TenascinC) %>% filter(TenascinC != 0) %>% summarize(Percent_Positive = mean(Percent_Positive)) %>%ggplot(aes(x = Abb_ECMs, y = Percent_Positive, col = TenascinC))+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_path(aes(group = TenascinC), linewidth = 1.5)+
  geom_point()+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("% Positive EdU")+
  scale_color_manual(values  = c("#c9462d", "#fa7152","#8dc1e1","#0f99ca","#07709f" 
)) +
  ylab("% EdU Positive")+
  theme(axis.text.x = element_text(angle = 90))

ggsave("TCTreatECM.png")

```



##P Heatmap
```{r}
heatmapFOC <- FOC[,c("Abb_ECMs", "Metadata_Slide", "Metadata_Experiment", "Metadata_Ratio", "Metadata_Stiffness", "Metadata_Treatment", "FOC")]

heatmapFOC <- heatmapFOC %>%filter(Metadata_Treatment != "DMSO")%>% group_by(Abb_ECMs, Metadata_Stiffness, Metadata_Treatment, Metadata_Ratio)%>%summarize(Mean_FOC = mean(FOC), .groups = "drop")

heatmapFOC <- heatmapFOC %>% mutate(TreatStiffness = paste(Metadata_Treatment, Metadata_Stiffness), Microenvironment = paste0(Abb_ECMs, Metadata_Ratio))

heatmapFOC <- heatmapFOC[,c("TreatStiffness" ,"Microenvironment", "Mean_FOC")]

heatmapFOC <- pivot_wider(data = heatmapFOC, names_from = "TreatStiffness", values_from = c("Mean_FOC"))
 
heatmapFOC <- as.matrix(heatmapFOC)

rownames(heatmapFOC) <- heatmapFOC[,1]

heatmapFOC <- heatmapFOC[,2:5]

heatmapFOC<- as.matrix(heatmapFOC)

class(heatmapFOC) <- "numeric"
```


```{r}
colann <- c("10 uM 1kPa" , "20 uM 1kPa" , "10 uM 25kPa" ,"20 uM 25kPa")

coldf <- data.frame(TreatStiff = colann)

coldf <- coldf %>% mutate(Treatment = if_else(TreatStiff %in% c("10 uM 1kPa",  "10 uM 25kPa"), "10 uM", "20 uM"), 
                                            
Stiffness = if_else(TreatStiff %in% c("10 uM 1kPa" , "20 uM 1kPa"), "1kPa", "25kPa"))
  
colgrouping <- data.frame(Treatment = coldf[,2],  Stiffness = coldf[,3], row.names = coldf[,1])
```

```{r}
library(pheatmap)

pheatmap(heatmapFOC, color = colorRampPalette(rev(brewer.pal(n=7, name = "RdBu")))(100), angle_col = 45, height = 15, width = 5, fontsize_row = 10, annotation_col = colgrouping, annotation_colors = list(
  Treatment = c("10 uM" = "#6c6768", "20 uM" = "#000000"), 
  Stiffness = c("1kPa"= "#db6d22", "25kPa" = "#2100bb")), filename = "FOCheatmapcol.png")

pheatmap(heatmapFOC, color = colorRampPalette(rev(brewer.pal(n=7, name = "RdBu")))(100), angle_col = 45, height = 15, width = 5, cluster_cols = FALSE, fontsize_row = 10, 
         annotation_col = colgrouping, annotation_colors = list(
 Treatment = c("10 uM" = "#6c6768", "20 uM" = "#000000"), 
  Stiffness = c("1kPa"= "#db6d22", "25kPa" = "#2100bb")),
         filename = "FOCheatmapnone.png")

```


## C1:LN 5050 & TC:HA 5050
```{r}
FOC %>% filter(Abb_ECMs == "C1:LN" & Laminin == 0.5) %>% ggplot(aes(x = Metadata_Stiffness, y = FOC))  +
  facet_grid(cols = vars(Metadata_Treatment)) +
  geom_boxplot(fill = "#35bebf")+
 stat_compare_means( label = "p.signif", size = 7, vjust = 0.5)+
  theme_prism(border = TRUE)+
  xlab("Ratio of Tenascin C")+
  ylab("Mean % EdU Positive") +
  ggtitle("C1:LN 50:50 ECM Combination") 

FOC %>% filter(Abb_ECMs == "TC:HA" & TenascinC == 0.5) %>% ggplot(aes(x = Metadata_Stiffness, y = FOC))  +
  facet_grid(cols = vars(Metadata_Treatment)) +
  geom_boxplot(fill = "#35bebf")+
 stat_compare_means( label = "p.signif")+
  theme_prism(border = TRUE)+
  xlab("Ratio of Tenascin C")+
  ylab("Mean % EdU Positive") +
  ggtitle("C1:LN 50:50 ECM Combination") 

#ggsave("C1LNBoxFOC.png", width = 10, height = 5)
```

## S:E:R Intx Plots
### 20 uM
natparkspallettes (acadia) for ratios
"#212E52", "#444E7E", "#8087AA", "#B7ABBC", "#F9ECE8", "#FCC893", "#FEB424", "#FD8700", "#D8511D"
```{r}
FOCECMmeansNuc$Laminin <- as.factor(FOCECMmeansNuc$Laminin)
FOCECMmeansNuc$CollagenI <- as.factor(FOCECMmeansNuc$CollagenI)
FOCECMmeansNuc$Hyaluronic_Acid <- as.factor(FOCECMmeansNuc$Hyaluronic_Acid)
FOCECMmeansNuc$CollagenIV <- as.factor(FOCECMmeansNuc$CollagenIV)
FOCECMmeansNuc$Galectin3 <- as.factor(FOCECMmeansNuc$Galectin3)

library(ggpubr)
library(ggprism)
FOCECMmeansNuc %>% filter(Metadata_Treatment == "20 uM") %>% group_by(Metadata_Stiffness, Abb_ECMs, Laminin) %>% filter(Laminin != 0) %>% summarize(Mean_FOC = mean(FOC)) %>% ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = Laminin))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Laminin, linetype = Laminin), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("Fraction of DMSO Control")+
  scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(c(0,1.6))+
  ggtitle("Laminin Ratio Over Stiffness and ECMs (20 uM)")

ggsave("StiffECMLNFOC20.png")

FOCECMmeansNuc %>% filter(Metadata_Treatment == "20 uM") %>% group_by(Metadata_Stiffness, Abb_ECMs, CollagenI) %>% filter(CollagenI != 0) %>% summarize(Mean_FOC = mean(FOC)) %>%ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = CollagenI))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = CollagenI, linetype = CollagenI), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("Fraction of DMSO Control")+
 scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(c(0,1.6))+
  ggtitle("Collagen I Ratio Over Stiffness and ECMs")
ggsave("StiffECMC1FOC20.png")

FOCECMmeansNuc %>% filter(Metadata_Treatment == "20 uM") %>% group_by(Metadata_Stiffness, Abb_ECMs, Galectin3) %>% filter(Galectin3 != 0) %>% summarize(Mean_FOC = mean(FOC)) %>%ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = Galectin3))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Galectin3, linetype = Galectin3), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("Fraction of DMSO Control")+
 scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(c(0,1.6))+
  ggtitle("Galectin 3 Ratio Over Stiffness and ECMs (20 uM)")
ggsave("StiffECMG3FOC20.png")

# FOCECMmeansNuc %>% group_by(Metadata_Stiffness, Abb_ECMs, Hyaluronic_Acid) %>% filter(Hyaluronic_Acid != 0) %>% summarize(Mean_FOC = mean(FOC)) %>%ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = Hyaluronic_Acid))+
#   facet_grid(cols = vars(Metadata_Stiffness))+
#   geom_path(aes(group = Hyaluronic_Acid, linetype = Hyaluronic_Acid), linewidth = 1.5)+
#   geom_point(size = 3)+
#   theme_prism(border = TRUE)+
#   xlab("ECM Composition")+
#   ylab("Fraction of DMSO Control")+
#   scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
#   scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
#   theme(axis.text.x = element_text(angle = 90))+
#   ggtitle("Hyaluronic Acid Ratio Over Stiffness and ECMs")
# ggsave("StiffECMHAFOC.png")
# 
# FOCECMmeansNuc %>% group_by(Metadata_Stiffness, Abb_ECMs, CollagenIV) %>% filter(CollagenIV != 0) %>% summarize(Mean_FOC = mean(FOC)) %>%ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = CollagenIV))+
#   facet_grid(cols = vars(Metadata_Stiffness))+
#   geom_path(aes(group = CollagenIV, linetype = CollagenIV), linewidth = 1.5)+
#   geom_point(size = 3)+
#   theme_prism(border = TRUE)+
#   xlab("ECM Composition")+
#   ylab("Fraction of DMSO Control")+
#   scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
#   scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
#   theme(axis.text.x = element_text(angle = 90))+
#   ggtitle("Collagen IV Ratio Over Stiffness and ECMs")
# ggsave("StiffECMC4FOC.png")
```
###10 uM
```{r}
library(ggpubr)
library(ggprism)

FOCECMmeansNuc %>% filter(Metadata_Treatment == "10 uM") %>% group_by(Metadata_Stiffness, Abb_ECMs, Laminin) %>% filter(Laminin != 0) %>% summarize(Mean_FOC = mean(FOC)) %>% ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = Laminin))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Laminin, linetype = Laminin), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("Fraction of DMSO Control")+
  scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(c(0,1.6))+
  ggtitle("Laminin Ratio Over Stiffness and ECMs  (10 uM)")

ggsave("StiffECMLNFOC10.png")

FOCECMmeansNuc %>% filter(Metadata_Treatment == "10 uM") %>% group_by(Metadata_Stiffness, Abb_ECMs, CollagenI) %>% filter(CollagenI != 0) %>% summarize(Mean_FOC = mean(FOC)) %>%ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = CollagenI))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = CollagenI, linetype = CollagenI), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("Fraction of DMSO Control")+
 scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(c(0,1.6))+
  ggtitle("Collagen I Ratio Over Stiffness and ECMs")
ggsave("StiffECMC1FOC10.png")

FOCECMmeansNuc %>% filter(Metadata_Treatment == "10 uM") %>% group_by(Metadata_Stiffness, Abb_ECMs, Hyaluronic_Acid) %>% filter(Hyaluronic_Acid != 0) %>% summarize(Mean_FOC = mean(FOC)) %>%ggplot(aes(x = Abb_ECMs, y = Mean_FOC, col = Hyaluronic_Acid))+
  facet_grid(cols = vars(Metadata_Stiffness))+
  geom_path(aes(group = Hyaluronic_Acid, linetype = Hyaluronic_Acid), linewidth = 1.5)+
  geom_point(size = 3)+
  theme_prism(border = TRUE)+
  xlab("ECM Composition")+
  ylab("Fraction of DMSO Control")+
 scale_color_manual(values  = c( "#444E7E", "#FEB424","#D8511D", "#8087AA")) +
  scale_linetype_manual(values = c("longdash", "solid", "twodash", "solid"))+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(c(0,1.6))+
  ggtitle("Hyaluronic Acid Ratio Over Stiffness and ECMs (10 uM)")
ggsave("StiffECMHAFOC10.png")

```

## Dot Plot Math
```{r}
library(dplyr)
FOC %>%filter(Metadata_Treatment != "DMSO") %>%filter(FOC < 1 & FOC > 0.5) %>% group_by(Metadata_Stiffness, Metadata_Treatment) %>% summarize(length(FOC))

FOCsumm %>% filter(Metadata_Treatment != "DMSO") %>%filter(FOC < 1 & FOC > 0.5) %>% group_by(Metadata_Stiffness, Metadata_Treatment) %>% summarize(length(FOC))
```

## Violin Plot FOC 
```{r}

FOCMeans <- FOC %>% group_by(Metadata_Stiffness, Conditions, Metadata_Treatment) %>% summarize(FOC = mean(FOC), .groups = "drop")

FOCCM <-  compare_means(FOC ~ Metadata_Stiffness, subset(FOC, Metadata_Treatment != "DMSO"), group.by = "Metadata_Treatment")

  ggplot()+
  facet_grid(cols = vars(Metadata_Treatment))+
  geom_violin(data = subset(FOC, Metadata_Treatment != "DMSO"),aes(x = Metadata_Stiffness, y = FOC)) + 
  geom_point(data = subset(FOCMeans, Metadata_Treatment != "DMSO"), aes(x = Metadata_Stiffness, y = FOC, group = Conditions), position = position_jitter(width = 0.2))+
 # scale_y_log10()+
  theme_prism()+
 theme(axis.text.x = element_text( size = 25),
        axis.title.x = element_text(size = 25),
        axis.text.y = element_text(size = 25), 
        axis.title.y = element_text(size = 25),
        legend.position = "none",
        plot.title = element_text(size =25),
        panel.background = element_blank(),
        strip.text = element_text(size = 25),
        panel.border = element_rect(colour = "black", fill=NA, size=1))+
    stat_pvalue_manual(FOCCM, y.position = 4, label = "p.signif", label.size = 10)+
  labs(title = "Fraction of DMSO Control",
       x = "Stiffness (kPa)",
       y = "Fraction of DMSO Control")
  ggsave(file = "StiffnessViolinFOC.png", width = 15, height = 8)
  
 
```
## FOC comparisons
```{r}
mycomparisons <- list(c("25/75", "50/50"), c("50/50", "75/25"), c("25/75", "75/25"))
ggplot(data = subset(FOC, Metadata_ECMs == "Collagen ILaminin" & Metadata_Treatment == "10 uM" & Metadata_Stiffness == "1kPa"), aes(x = Metadata_Ratio, y = FOC))+
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness))+
  geom_boxplot(fill = "#89b94b") + 
  theme_prism()+
  stat_compare_means(comparisons = mycomparisons, label = "p.signif", size = 7, vjust = 0.5, hide.ns = TRUE)+
    theme(legend.position = "none",
          panel.border = element_rect(colour = "black", fill=NA, size=1))+
  labs(title = "Fold Change from DMSO on C1LN \n 10 uM 1 kPa",
       x = "ECM Ratio",
       y = "Fold Change from DMSO")
  ggsave(file = "C1LN.png", width = 5, height = 5)
  
  ggplot(data = subset(FOC, Metadata_ECMs == "Tenascin CFibronectin" 
                        & Metadata_Treatment == "20 uM" & Metadata_Stiffness == "1kPa"), aes(x = Metadata_Ratio, y = FOC))+
  facet_grid(cols = vars(Metadata_Treatment), rows = vars(Metadata_Stiffness))+
  geom_boxplot(fill = "#e0a852") + 
  theme_prism()+
    theme(legend.position = "none",
          panel.border = element_rect(colour = "black", fill=NA, size=1))+
  stat_compare_means(comparisons = mycomparisons, label = "p.signif", size = 7, vjust = 0.5, hide.ns = TRUE)+
  labs(title = "Fold Change from DMSO on TCFN \n 20 uM 1 kPa",
       x = "ECM Ratio",
       y = "Fold Change from DMSO")
  ggsave(file = "TCFN.png", width = 5, height = 5)
```

